---
title: "Introduction to week4assignment"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars-demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  eval = FALSE
)
```

```{r setup}
library(week4assginment)
```

The __week4assginment__ package provides functions to read, summarize and visualize data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System (FARS), which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. 

## 1. Data reading 

The funciton `fars_read_years()` reads FARS data for a single year or a list of years (an integer or a string). A `tbl_df` object or a list of such object will be returned. 

```{r}
data1 <- fars_read_years(2013)
data2 <- fars_read_year(c(2013, 2014))
data3 <- fars_read_year("2013")
```

Alternatively, data from an specific year can be read by parsing in the filename constructed by `make_filename()` to `fars_read()`. 

```{r}
fn <- make_filename(2013)
data4 <- fars_read(fn)
```

## 2. Data summary 

The __week4assignment__ package also provides the function `fars_summarize_year()` to summarize the number of accidents in each month for specific years. 

```{r}
summary_table1 <- fars_summarize_years(2013)
summary_table2 <- fars_summarize_years(c(2013, 2014))
summary_table3 <- fars_summarize_years("2013")
```

## 3. Data visualization 
The function `fars_map_state()` can be used to plot the locations of accidents for a specific state in a year. States are numbered 1 to 51. A plot will be made which shows a map of the state of interest, and dots representing 

```{r}
fars_map_state(1, 2013)
fars_map_state(19, 2014)
```
